Developing a preprint culture in biology

### 2013-03-06 ms.tex
last corrections

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}
    \begin{tabular}{|l|cccccccc|}
    \hline
    Website               & Free & Comments & Private preprints & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
    peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \begin{flushleft}
    \textbf{Free:} Whether preprints can be submitted for free.
    \textbf{Comments:} Support for online comments on the item.
    \textbf{Private:} Support for private preprints.
    \textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
    \textbf{DOI:} Each item is assigned a unique digital object identifier.
    \texbbf{Version-Control:} Is the preprint stored with a version-control system with the complete history of modifications?
    \textbf{Other content:} Can upload figures, videos, datasets, code.
    \end{flushleft}
    \label{table:box1}
\end{table}

>>>>

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}
    \begin{tabular}{|l|ccccccc|}
    \hline
    Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
    peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \begin{flushleft}
    \textbf{Free:} Can preprints be submitted for free.
    \textbf{Comments:} Support for online comments.
    \textbf{Private:} Support for private preprints.
    \textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
    \textbf{DOI:} Each item is assigned a unique digital object identifier.
    \textbf{Version-Control:} Is the preprint stored using a version-control system with the complete history of modifications?
    \textbf{Other content:} Can upload figures, videos, datasets, code.
    \end{flushleft}
    \label{table:box1}
\end{table}
